### 2022-03-03 README.Rmd
Add DOI for zenodo upload.

@@

> Henning Teickner and Klaus-Holger Knorr, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r manuscript1_yaml$title`" and "`r manuscript2_yaml$title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://github.com/henningte/hklmirs/>

@@

You can download the compendium as a zip from from this URL: <https://github.com/henningte/hklmirs/>

>>>>

[![DOI](https://zenodo.org/badge/465653387.svg)](https://zenodo.org/badge/latestdoi/465653387)

@@

> Henning Teickner and Klaus-Holger Knorr, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for "`r manuscript1_yaml$title`" and "`r manuscript2_yaml$title`"_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.6325760>

@@

You can download the compendium as a zip from from these URLs: <https://github.com/henningte/hklmirs/> or <https://doi.org/10.5281/zenodo.6325760>
